---
title: "Creating a Personal Style Guide"
author: "Kartik Midha"
format: revealjs
scrollable: true
editor: visual
---

## File names

-   Use a meaningful and descriptive names

-   End in .R

    -   rmd - for RMarkDown files

    -   qmd- for Quarto files

-   Preferably use camelCase

-   If necessary, separate words by \_ not .

-   Files should be stored in a meaningful directory

------------------------------------------------------------------------

```{r}
#| eval: false
#| echo: true
#| paged-print: true

# Example for good file name
getData.R
predict_ad_revenue.R

# Acceptable file name
get_data.R
predictAdRevenue.R

# Example for bad file name
foo.bar.r
u111.r
predictadrevenue.R

```

------------------------------------------------------------------------

-   Specific File Locations

```{r}
#| eval: FALSE
#| echo: true

# This might work on one machine, but not another:

load("c:/user/kmidha/RProject/Project1/myData.RData")

# This will work on all machines if placed in the project folder:

load("myData.RData")

```

## Object names

-   R is case sensitive

-   Use names to clarify the meaning

-   Try to be consistent for names

-   Use \_ while naming variable or function name; . is used by default by R in naming

------------------------------------------------------------------------

```{r}
#| echo: true

# Good

student_score <- c(10, 12, 14, 15, 11, 20, 19, 7)

score_mean <- mean(student_score)

score_sd <- sd(student_score)

# Bad

st_sc <- c(10,12,14,15,11,20,19,7)

mean_s <- mean(student_score)

s_sd <- sd(student_score)

```

## Use of upper and lower case

-   Since R is case sensitive; *variable_name* and *Variable_name* is different

-   Change case or use CamelCase if not using \_ or .

```{r}
#| echo: true

# Confusing

studentscore <- c(10,12,14,15,11,20,19,7)

# Good

StudentScore <- c(10, 12, 14, 15, 11, 20, 19, 7)

studentScore <- c(10, 12, 14, 15, 11, 20, 19, 7)
```

## Spacing

-   Place spaces around all binary operators such as =, +, -, \<-, \*, etc.

-   Place a space before the ( , except in a function call

-   Use space after a comma

------------------------------------------------------------------------

```{r}
#| echo: true

# This isn't terrible:

feet<-c(10,12,13,14,15)
inches<-c(1,5,6,8,8)
average<-mean(feet/12+inches,na.rm=TRUE)

# But this is better:

feet <- c(10, 12, 13, 14, 15)

inches <- c(1, 5, 6, 8, 8)

average <- mean(feet / 12 + inches, na.rm=TRUE)

```

------------------------------------------------------------------------

-   Consistency

```{r}
#| echo: true

# Notice the consistent spacing in these comments which would not be
# so good if I suddenly started creating comments
#like this
#      or like this.
```

## Line length

-   Keep each line less than 80 characters

```{r}
#| echo: true

# This is an example of a line that has gone on too long so that it will wrap around and make it difficult to read and introduce an inconsistency with the way we are creating comments.

# This is an example of a line that has not gone on too long so that it
# we did a wrap around with additional hashtags to make our comments
# consistent.

```

------------------------------------------------------------------------

-   Align lines by shared features like parameters if possible

```{r}
#| eval: FALSE
#| echo: true

# Good
someFunction(optionA = alpha,
             optionB = bravo,
             optionC = charlie,    
             optionD = delta)

# Acceptable
someFunction(optionA = alpha,
    optionB = bravo, optionC = charlie,    
    optionD = delta)

# Bad
someFunction(optionA = alpha, optionB = bravo, optionC = charlie, optionD = delta)
```

## Indentation

-   Be consistent for better presentation and avoiding confusion

```{r}
#| echo: true

# Here's an example of no indentation, making it difficult to understand
# how this data frame has different items :

our_data_frame <- data.frame(name = c("Joe", "Sue", "Brian"), age = c(28, 32, 45), enrolled = c(FALSE, TRUE, TRUE))

# Look how much nicer this is and easily readable:

our_data_frame <- data.frame(name = c("Joe", "Sue", "Brian"),
                             
                             age = c(28, 32, 45),
                             
                             enrolled = c(FALSE, TRUE, TRUE))
```

## Assignment operations

-   Using = to assign can be confusing

-   Use \<- to assign

-   It is better to write the variable/function name on the left

```{r}
#| echo: true

# This works, but it can be confusing:

StudentScores = c(34, 39, 41, 37, 39, 28)

c(34, 39, 41, 37, 39, 28) -> StudentScores

# No confusion here:

StudentScores <- c(34, 39, 41, 37, 39, 28)

```

## Commenting

-   General comments should be identified with \# followed by a space

-   Inline comments need 2 spaces before the \#

-   Function and object descriptions should adhere to roxygen guidelines

-   Separate function comments and function code with blank line

-   Functions from previous code using 2 blank lines

------------------------------------------------------------------------

```{r}
#| echo: true

# An example of a useful comment:

## Checking how many students have scores greater than 10

student_score <- c(10,12,14,15,11,20,19,7)

ScoreAbove10 <- sum(student_score > 10)

# An example of a comment that is not very useful:

## Setting StudentMean to 6

StudentMean <- 6

```
